### 2017-10-13 Gruba/02-overview.tex

\begin{definition}
\label{def:blog}
A microblog $M_b = (O, T, M, flag)$ has its owner $O$ (a.k.a. user in this paper) to whom $M_b$ belongs (either created or \retd{}), the generated time $T$ of $M_b$, the message context $M$, and $flag$ denoting $M_b$ is \retd{} (1) or originally \tw{} (0) by $O$.
\end{definition}

>>>>

\begin{definition}
\label{def:blog}
A microblog $M_b = (O, T, M, flag)$ has its owner $O$ (a.k.a. user in this paper) to whom $M_b$ belongs (either \twd{} or \retd{}), the generated time $T$ of $M_b$, the message context $M$, and $flag$ denoting $M_b$ is \retd{} (1) or originally \tw{} (0) by $O$.
\end{definition}
